---
title: "R objects, Workflow, and Functions"
format: html
editor: visual
---

# Vectors
Create a vector

```{r}
set.seed(42)
my_unif <- runif(30)
is.vector(my_unif)
```
Sebset that object

```{r}
my_unif[1:10]
my_unif[c(1:3, 15:17)]
```

Sort the vector

```{r}
sort(my_unif)
```
Create a vector with strings in it.(number first, lower case then, last upper case)

```{r}
char_vec <- c('daf', "adf", "E2", '13da')
sort(char_vec)
```
# Data Frame

```{r}
data(trees)
trees
str(trees)
```
Subset a column

```{r}
trees$Height
```
Get attributes from the data frame

```{r}
attributes(trees)
names(trees)
colnames(trees)[2:3]
```
# Lists

Inevestigating data frame from before

```{r}
is.list(trees)
is.data.frame(trees)
```
Can subset as a list

```{r}
trees[1:2]
trees[[2]]
```
Look at linear model fit

```{r}
fit  <- lm(Volume ~ Height + Girth, data = trees)
```

Look at structure but restrict info (1st level of structure):

```{r}
str(fit, max.level = 1)
```
Some helper functions exist 

```{r}
fit$coefficients
coef(fit)
fit$residuals
residuals(fit)
```

